Application of Micro-Rotors to Induce Crystal Nucleation: Challenges, Takeaways, and Future Prospects\\ PhD Thesis

### 2025-08-14 Latex_files/Thesis/chapters/chapter 2/main.tex
14/08/25 changes, chp 5 done (ref needed)

\chapter{Theory and methods}
\label{chapter:theory}
\textit{\textbf{Add overview here}} \\
This chapter covers the theory behind light and particle interactions, 
and how the exact theory varies for differently sized particles. After 
that we show how this can be applied to existing diffusion models to 
accurately simulate the behaviour of a particle within the vicinity of 
an optical trap. Lastly, we highlight the techniques utilised in 
experiments to both calibrate and characterise an optical trap based 
on our understanding of the trap.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Harmonic Traps}
\label{sec:harmonic_traps}
When a sphere is located at the centre of a laser the gradient 
force will try to recentre the sphere if it is displaced. If 
the restoring force is proportional to the sphere's displacement 
this is referred to as a harmonic trap. The ratio of the restoring 
force to the displacement is called the trap stiffness (denoted 
by $\kappa$), and is an important characteristic of the trap. Fig.~\ref{fig:harmonic_trap} demonstrates an example case of the
force-displacement curve for a simple sphere in an optical trap. 
Laser power and numerical aperture are omitted as the exact shape 
is not of importance, only the linear region about the origin.
\begin{figure}[h!]
	\centering
	\includegraphics[width=1.1\linewidth]{sphere_force_curve.png}
	\caption{Example of a sphere's ($r=1\ \mu m$) force-displacement
		curve while moving along the x-axis, where $x=0$ is the 
		centre of the beam. The harmonic regime is highlight by the 
		linear fit given in black.}
	\label{fig:harmonic_trap}
\end{figure}

The strength of the optical trap is directly proportional to 
both the laser power and the contrast in refractive indices 
between the medium and the particle. Fully describing the 
optical forces is dependent on the ratio between the particle 
size ($a$) and the trapping wavelength ($\lambda$). The 
scattering theory that describes the optical force is dependent 
on this ratio.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lornez-Mie Theory}

@@

Where the matrix \textbf{T} accounts for the targets shape, 
and refractive index. The $T$-matrix method can be easily 
applied to any solution of Maxwell's equations. In order to compute 
the optical force and torque applied to a given object one simply 
needs to know the momentum carried by the incident and scattered 
fields. So long as we know the expansion coefficients of the 
incident beam we can find the scattered beam coefficients via Eq.~\eqref{eq:t_matrix} to compute the force.

And the time averaged linear momentum carried by the scattered 
beam is given by:
\begin{equation}
	\label{eq:linear_momentum_out}
	\begin{split}
		\langle P_{z,\ out} \rangle
		&=
		-\frac{1}{4\pi k^2}\sum_{n,m} \left(\frac{m}{n(n+1)}\Im[p_{nm}q^*_{nm}] \right.
		\\ 
		&+\frac{1}{n+1}\left[\frac{n(n+2)(n-m+1)(n+m+1)}{(2n+1)(2n+3)} \right]^{1/2}
		\\
		& \left.\times\Im[q_{nm}q^*_{nm}+p_{nm}p^*_{n+1m}] \right)
	\end{split}
\end{equation}

@@

\noindent
Where $a_{nm}, b_{nm}, p_{nm}, \& q_{nm}$ are the beam expansion 
coefficients used in \eqref{eq:incident} \& \eqref{eq:scattered}.
Similar expressions are shown in Sec.~\ref{sec:simulations} for 
calculating the optical torque. Lorenz-Mie theory can be applied 
to describe the scattering from any particle regardless of size.
Though as the size of the target particle changes - relative to 
the wavelength of light - the theory describing the electromagnetic 
fields are easier to approximate by alternative theories. When the 
particle radius is $\gg \lambda$ the optical force is best described 
by the Ray-Optics model. In the opposite case the target particle is 
better approximated as a single electric dipole as described by 
the Rayleigh approximation.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{T-matrix Method}
The $T$-matrix method was first developed by Peter Waterman with 
his research into acoustic wave scattering \cite{Waterman1969}, 
this would later be extended to electromagnetic waves. Sometimes 
referred to as the extended boundary condition method (EBCM), the 
method replaces the scatterer with a series of surface currents 
over the targets surface. These currents are chosen so that the 
electromagnetic field outside is identical to the original problem 
\cite{Wriedt1998}. By expanding the harmonic functions one can 
derive the individual elements of \textbf{T} until a desired 
accuracy is achieved. One can either use the EBCM to compute the 
scattering for a fixed particle orientation and position. Or they
can evaluate the scattering for any particle orientation by 
computing its $T$-matrix. Because the T-matrix is based only 
on the properties of the scatterer it can be reused in 
calculations regardless of the incident field in question.

@@

The Ray-Optics model is the simplest to understand, this theory models 
the electromagnetic field as a collection of individual 'rays' that 
propagate and are refracted according to Snell's Law. Based on the 
change in direction momentum is transferred to the target particle; 
with rays closest to the centre of the beam having greater intensity 
than those rays at the very edge of the beam. Consider a particle 
struck by two rays in a Gaussian beam, one coming close to the centre, 
and the other ray coming from the edge. As each ray is refracted by 
the target sphere a force is imparted onto it, the total force 
imparted is given by:
\begin{align}
	F_i = Q_i\frac{\Delta n P_i}{c}
\end{align}

\noindent 
where $Q_i$ is the trapping efficiency, $\Delta n$ is the difference
in refractive indices between the solution and the target particle,
and $P_i$ is the power of the individual ray. The net force can be 
subdivided into its gradient and scattering components, where the latter
directs the particle to the centre of the beam, and the former acts on 
the particle in the direction of beam propagation. For a beam with a
Gaussian intensity distribution $P_i$ will fall off as you move from
the centre of the beam. The ray optics model is ideal when dealing 
with larger particles whose diameter far exceed the wavelength of light
being scattered. While it can be useful in predicting the forces 
experienced by said particle's it does not fully capture the behaviour
of light when considering interference between different rays. And 
as such no information is learned about the scattered field.

@@

The Rayleigh approximation is for describing a particle when 
the particle radius is $\ll \lambda$. The underlying theory 
is that a dielectric sphere can be treated as a dipole while 
in the presence of the electromagnetic field. In which case 
the scattering force is given simply by the scattering of 
the induced dipole, and the gradient force is due to the 
Lorentz force \cite{Gordon1973}. The gradient forces in the 
principle Cartesian axis are described by Harada et al \cite{YasuhiroHarada1996} in MKS units as a restorative 
rectangular force field:
\begin{align}
  F_{grad,x}
  &=-\hat{x} \frac{2\pi n_2 a^3}{c}
    \left(\frac{m^2-1}{m^2+2}\right) \frac{4\tilde{x}/w_0}{1+(2\tilde{z})^2} \times I(r)
  \label{eq:Rayleigh_start}\\
  F_{grad,y}
  &=-\hat{y} \frac{2\pi n_2 a^3}{c}
    \left(\frac{m^2-1}{m^2+2}\right) \frac{4\tilde{y}/w_0}{1+(2\tilde{z})^2} \times I(r)
  \\
  F_{grad,z}
  &=-\hat{z} \frac{2\pi n_2 a^3}{c}
    \left(\frac{m^2-1}{m^2+2}\right) \frac{4\tilde{z}/w_0}{1+(2\tilde{z})^2}
    \nonumber \times I(r)
  \\ 
  & \times \left[1-\frac{2(\tilde{x}^2+\tilde{y}^2)}{1+(2\tilde{z})^2} \right]
  \\
  \label{eq:Rayleigh_end}
\end{align}
where, for a approximate Gaussian beam the intensity $I(r)$ 
close to the beam focus can be calculated as such.
\begin{align}
  \nonumber
	I(r) &= \left(\frac{2P}{\pi w_0^2}\right) \frac{1}{1+(2\tilde{z}^2)} 
	\exp \left[ - \frac{2(\tilde{x}^2+\tilde{y}^2)}{1+(2\tilde{z})^2} \right]
\end{align}

@@

\subsection{Langevin Equation}
Describing any microscopic motion requires an understanding 
of a molecules diffusive behaviour, for the case of optical 
tweezers the most complete model of diffusion is the Langevin 
equation. Models such as the Fickian, and Einstein derivations 
are sufficient for macroscopic behaviours but the Langevin 
model better describes the microscopic characteristics of 
any diffusive behaviour.

@@

The Langevin model of diffusion assumes that the net force on 
a particular particle is described fully by these individual 
collisions \cite{Gillespie2012c}. Unlike the Fickian model it 
provides a full description of the interactions between the 
target molecule and the surrounding fluid; while also being 
able to describe its motion over any time scale, unlike the 
Einstein model. The standard form of the Langevin model for 
a particle undergoing Brownian motion is given as:
\begin{align}
	m\frac{dv}{dt} + \gamma_0 v + F(t) = W(t)
\end{align}

@@

Where $w_i$ is a random real number between -1 and 1, we can say 
that it is normally distributed around 0 for simulation purposes. 
We can rearrange this for $x_i$ to approximate the Brownian motion 
of a particle (setting $x_0=0$), where the characteristic time is 
$\tau = m/\gamma$. Now in the case of an optical trap, the 
restoration time scale is given by $\tau_{OT}=\kappa_x/\gamma$ 
which for strongly trapped particles is far greater than the 
characteristic time. As such we can neglect the particle's inertia 
which allows the motion of an optically trapped particle to be written 
as:
\begin{align}
	\label{eq:sim_langevin}
	x_i = x_{i-1} - \tau_{OT}\ x_{i-1}\Delta t + \sqrt{2D\Delta t}\ w_i
\end{align}

@@

Using a  MATLAB package called \textit{Optical Tweezer Toolbox} 
or \textit{ott} \cite{Nieminen2007} we can compute the beam 
shape coefficients ($a_{nm}$ \& $b_{nm}$) for any desired beam 
type. Using the results from \cite{Farsund1996} we can then 
compute both the optical force and torque using the beam 
coefficients and the scattering coefficients ($q_{nm}$ \& $p_{nm}$) 
which are found by calculating the dimer's $T$-matrix via \textit{mstm} 
\cite{Mackowski2011} and then using \eqref{eq:t_matrix}. The 
total force in along the z-direction and the total torque about 
the z-axis are provided:
\begin{equation}
	\label{eq:optical_force}
	\begin{split}
		\bold{F_z}
		&=
		-\frac{1}{4\pi k^2}\sum_{n,m} \left(\frac{m}{n(n+1)}\Im[a_{nm}b^*_{nm}-p_{nm}q^*_{nm}] \right.
		\\ 
		&+\frac{1}{n+1}\left[\frac{n(n+2)(n-m+1)(n+m+1)}{(2n+1)(2n+3)} \right]^{1/2}
		\\
		& \left.\times\Im[b_{nm}b^*_{nm}+a_{nm}a^*_{n+1m}-q_{nm}q^*_{nm}+p_{nm}p^*_{n+1m}] \right)
	\end{split}
\end{equation}
\begin{equation}
	\begin{split}
		\bold{T_z}
		&=
		-\frac{1}{8\pi k^3}\sum_{n,m} \left(\frac{m}{n(n+1)}[|a_{nm}|^2+|b_{nm}|^2-|p_{nm}|^2-|q_{nm}|^2] \right.
		\\ 
		&+\frac{2}{n+1}\left[\frac{n(n+2)(n-m+1)(n+m+1)}{(2n+1)(2n+3)} \right]^{1/2}
		\\
		& \left.\times\Re[b_{nm}a^*_{nm}+a_{nm}b^*_{n+1m}-p_{nm}q^*_{nm}+q_{nm}p^*_{n+1m}] \right)
	\end{split}
\end{equation}

where $a_{nm}$, $b_{nm}$, $p_{nm}$, and $q_{nm}$ are the beam 
coefficients of the incident and scattered fields respectively. 
We can get the $x$ and $y$ force and torque components in a 
similar form by applying a simple rotation transformation. With 
the optical forces and torques computed all that remains is to 
compute the Brownian forces and torques which are constrained 
by the relation.
\begin{align}
	\langle q_iq_j\rangle =2D_{ij}\Delta t
\end{align}

Vigilante et al compiled together a python package that combines 
both \textit{ott} and \textit{mstm} to simulate the behaviour of 
spherical aggregates within a predefined optical trap 
\cite{Vigilante2020}. Now \textit{ott} does have inbuilt $T$-matrix 
modules that can be used to model the scattering from different 
shaped particles; however, for aggregates of spheres the resultant 
force is nonsensical (see Chapter 4 for further details). As such 
we rely on the \textit{mstm} for simulating dimers.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

If we use \eqref{eq:anylitical_lang} for an optical tweezer we can 
expand out the squared term to get an analytical expression for the 
MSD as a function of time lags:
\begin{align}
	\label{eq:MSD}
	MSD(\tau) = \left<|x(t+\tau)^2-2x(t+\tau)x(t)+x(t)^2|\right> = \frac{2k_BT}{\kappa_x}\left[1-e^{-\frac{\tau}{\tau_{OT}}}\right]
\end{align}

>>>>

\chapter{Theory and methods}
\label{chapter:theory}
This chapter covers the theory behind light and particle interactions, 
and how the exact theory varies for differently sized particles. After 
that we show how this can be applied to existing diffusion models to 
accurately simulate the behaviour of a particle within the vicinity of 
an optical trap. Lastly, we highlight the techniques utilised in 
experiments to both calibrate and characterise an optical trap based 
on our understanding of the trap.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lornez-Mie Theory}

@@

Where the matrix \textbf{T} accounts for the targets shape, 
and refractive index. The $T$-matrix method can be easily 
applied to any solution of Maxwell's equations. The $T$-matrix
method allows us to relate directly the momentum carried by 
the incoming wave \ref{eq:incident} to the momentum retained
by the scattered wave \ref{eq:scattered}, where the difference 
between these two quantities is the momentum transferred to
the scattering object. The time averaged change change in 
this momentum transfer provides an approximation of the force 
imparted to the target scatterer.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{TO BE MOVED}
And the time averaged linear momentum carried by the scattered 
beam is given by:
\begin{equation}
	\label{eq:linear_momentum_out}
	\begin{split}
		\langle P_{z,\ out} \rangle
		&=
		-\frac{1}{4\pi k^2}\sum_{n,m} \left(\frac{m}{n(n+1)}\Im[p_{nm}q^*_{nm}] \right.
		\\ 
		&+\frac{1}{n+1}\left[\frac{n(n+2)(n-m+1)(n+m+1)}{(2n+1)(2n+3)} \right]^{1/2}
		\\
		& \left.\times\Im[q_{nm}q^*_{nm}+p_{nm}p^*_{n+1m}] \right)
	\end{split}
\end{equation}

@@

\noindent
Where $a_{nm}, b_{nm}, p_{nm}, \& q_{nm}$ are the beam expansion 
coefficients used in \eqref{eq:incident} \& \eqref{eq:scattered}.
Similar expressions are shown in Sec.~\ref{sec:simulations} for 
calculating the optical torque. Lorenz-Mie theory can be applied 
to describe the scattering from any particle regardless of size.
Though as the size of the target particle changes - relative to 
the wavelength of light - the theory describing the electromagnetic 
fields are easier to approximate by alternative theories. When the 
particle radius is $\gg \lambda$ the optical force is best described 
by the Ray-Optics model. In the opposite case the target particle is 
better approximated as a single electric dipole as described by 
the Rayleigh approximation.

\textbf{END OF TO BE MOVED}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{T-matrix Method}
The $T$-matrix method was first developed by Peter Waterman with 
his research into acoustic wave scattering \cite{Waterman1969}, 
this would later be extended to electromagnetic waves. Sometimes 
referred to as the extended boundary condition method (EBCM), the 
method replaces the scatterer with a series of surface currents 
over the targets surface. These currents are chosen so that the 
electromagnetic field outside is identical to the original problem 
\cite{Wriedt1998}. By expanding the harmonic functions one can 
derive the individual elements of \textbf{T} until a desired 
accuracy is achieved. One can either use the EBCM to compute the 
scattering for a fixed particle orientation and position. Or they
can evaluate the scattering for any particle orientation by 
computing its $T$-matrix. Because the T-matrix is based only 
on the properties of the scatterer it can be reused in 
calculations regardless of the incident field in question.

This is in truth merely an extension of the Lorenz-Mie theory 
as the T-matrix of a single sphere can be found from the electric 
field solutions. The method developed by Waterman allows for any 
arbitrary shaped particle to produce similar solutions. One of 
the biggest advantages to the method is the fact that it can 
leverage symmetries in particle geometries to speed up calculations.

@@

The Ray-Optics model is the simplest to understand, this theory models 
the electromagnetic field as a collection of individual 'rays' that 
propagate and are refracted according to Snell's Law. The Ray optics
model is generally only used in cases where the particle size is far
greater than the wavelength of light  Based on the change in direction 
momentum is transferred to the target particle; with rays closest to 
the centre of the beam having greater intensity than those rays at the 
very edge of the beam. Consider a particle struck by two rays in a 
Gaussian beam, one coming close to the centre, and the other ray 
coming from the edge. As each ray is refracted by the target sphere a 
force is imparted onto it, the total force imparted is given by:
\begin{align}
	F_i = Q_i\frac{\Delta n P_i}{c}
\end{align}

\noindent 
where $Q_i$ is the trapping efficiency, $\Delta n$ is the difference
in refractive indices between the solution and the target particle,
and $P_i$ is the power of the individual ray. The net force can be 
subdivided into its gradient and scattering components, where the latter
directs the particle to the centre of the beam, and the former acts on 
the particle in the direction of beam propagation. For a beam with a
Gaussian intensity distribution $P_i$ will fall off as you move from
the centre of the beam. While the ray optics model can be useful in 
predicting the forces experienced by said particle's it does not fully 
capture the behaviour of light when considering interference between 
different rays. And as such no information is learned about the scattered 
field.

@@

The Rayleigh approximation is for describing a particle when 
the particle radius is $\ll \lambda$, as the particle shape 
decreases we find the effective scattered area approaches 
zero as the incident light diffracts around the target particle. 
As such we can approximate a dielectric sphere as a dipole while 
in the presence of the electromagnetic field. In which case the 
scattering force is given simply by the scattering of the induced 
dipole, and the gradient force is due to the Lorentz force 
\cite{Gordon1973}. The gradient forces in the principle Cartesian 
axis are described by Harada et al \cite{YasuhiroHarada1996} in MKS 
units as a restorative rectangular force field:
\begin{align}
  F_{grad,x}
  &=-\hat{x} \frac{2\pi n_2 a^3}{c}
    \left(\frac{m^2-1}{m^2+2}\right) \frac{4\tilde{x}/w_0}{1+(2\tilde{z})^2} \times I(r)
  \label{eq:Rayleigh_start}\\
  F_{grad,y}
  &=-\hat{y} \frac{2\pi n_2 a^3}{c}
    \left(\frac{m^2-1}{m^2+2}\right) \frac{4\tilde{y}/w_0}{1+(2\tilde{z})^2} \times I(r)
  \\
  F_{grad,z}
  &=-\hat{z} \frac{2\pi n_2 a^3}{c}
    \left(\frac{m^2-1}{m^2+2}\right) \frac{4\tilde{z}/w_0}{1+(2\tilde{z})^2}
    \nonumber \times I(r)
  \\ 
  & \times \left[1-\frac{2(\tilde{x}^2+\tilde{y}^2)}{1+(2\tilde{z})^2} \right]
  \\
  \label{eq:Rayleigh_end}
\end{align}
where, for a approximate Gaussian beam the intensity $I(r)$ 
close to the beam focus can be calculated as such.
\begin{align}
  \nonumber
	I(r) &= \left(\frac{2P}{\pi w_0^2}\right) \frac{1}{1+(2\tilde{z}^2)} 
	\exp \left[ - \frac{2(\tilde{x}^2+\tilde{y}^2)}{1+(2\tilde{z})^2} \right]
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Diffusion Models}
For the case of optical tweezers the most complete model of 
diffusion is the Langevin equation. Models such as the Fickian, 
and Einstein derivations are sufficient for macroscopic 
behaviours but the Langevin model better describes the 
microscopic characteristics of any diffusive behaviour.

@@

The Langevin model of diffusion assumes that the net force on 
a particular particle is described fully by these individual 
collisions \cite{Gillespie2012c}. Unlike the Fickian model it 
provides a full description of the interactions between the 
target molecule and the surrounding fluid; while also being 
able to describe its motion over any time scale, unlike the 
Einstein model. Unlike the Einstein model that views collisions
as discrete but finite events, the Langevin model instead 
considers the collisions as one random The standard form of the 
Langevin model for a particle undergoing Brownian motion is 
given as:
\begin{align}
	m\frac{d\vec{v}}{dt} = - \gamma_0 \vec{v} + F(t) + W(t)
\end{align}

@@

Where $w_i$ is a Gaussian random real number between -1 and 1, we 
can say that it is normally distributed around 0 for simulation purposes. 
We can rearrange this for $x_i$ to approximate the Brownian motion 
of a particle (setting $x_0=0$), where the characteristic time is 
$\tau = m/\gamma$. Now in the case of an optical trap, the 
restoration time scale is given by $\tau_{OT}=\kappa_x/\gamma$ 
which for strongly trapped particles is far greater than the 
characteristic time. As such we can neglect the particle's inertia 
which allows the motion of an optically trapped particle to be written 
as:
\begin{align}
	\label{eq:sim_langevin}
	x_i = x_{i-1} - \tau_{OT}\ x_{i-1}\Delta t + \sqrt{2D\Delta t}\ w_i
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Harmonic Traps}
\label{sec:harmonic_traps}
When a sphere is located at the centre of a laser the gradient 
force will try to recentre the sphere if it is displaced. If 
the restoring force is proportional to the sphere's displacement 
this is referred to as a harmonic trap. The ratio of the restoring 
force to the displacement is called the trap stiffness (denoted 
by $\kappa$), and is an important characteristic of the trap. 
Fig.~\ref{fig:harmonic_trap} demonstrates an example case of the
force-displacement curve for a simple sphere in an optical trap. 
Laser power and numerical aperture are omitted as the exact shape 
is not of importance, only the linear region about the origin.
\begin{figure}[h!]
	\centering
	\includegraphics[width=1.1\linewidth]{sphere_force_curve.png}
	\caption{Example of a sphere's ($r=1\ \mu m$) force-displacement
		curve while moving along the x-axis, where $x=0$ is the 
		centre of the beam. The harmonic regime is highlight by the 
		linear fit given in black.}
	\label{fig:harmonic_trap}
\end{figure}

The strength of the optical trap is directly proportional to 
both the laser power and the contrast in refractive indices 
between the medium and the particle. Fully describing the 
optical forces is dependent on the ratio between the particle 
size ($a$) and the trapping wavelength ($\lambda$). The 
scattering theory that describes the optical force is dependent 
on this ratio.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

If we sub in \eqref{eq:anylitical_lang} for $x(t)$ we can expand 
out the squared term to get an analytical expression for the MSD 
as a function of time lags:
\begin{align}
	\label{eq:MSD}
	MSD(\tau) &= \left<|x(t+\tau)^2-2x(t+\tau)x(t)+x(t)^2|\right> \\
	\rightarrow MSD(\tau) &=\frac{2k_BT}{\kappa_x}\left[1-e^{-\frac{\tau}{\tau_{OT}}}\right]
\end{align}
